### 2014-11-11 tex/bisimulation.tex
Minor tweak on last paragraph

The relation, $P \sqsubset q$, is readily established in the initial
state of a given program, as there is single initial state, $P_o =
\{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
then defined as $q_o = p_o$; $P_o \sqsubset q_o$ is trivially shown.

>>>>

The relation, $P \sqsubset q$, is readily established in the initial
state of a given program as there is single initial state, $P_o =
\{p_o\}$, in any valid Javalite program. The initial state for $\rsym$ is
then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.
